---
title: "Analysis of Accident Data"
author: "Oliver Dietz"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, message=FALSE, echo=FALSE}
devtools::load_all()
```

## Introduction 
This package allows to summarise and plot US accident data through two main wrapper functions:

- ``fars_summarize_years()`` counts the number observations in each month of the specified year.
- ``fars_map_state()`` plots the accident locations on a map of the specified state and year.

The package comes with a couple of helper functions that enable you to read accident files from several years. They are also used under the hood of the two main wrapper functions.

- ``make_filename()`` creates a filename following the pattern "accident_YEAR.csv.bz2", e.g. ``accident_2013.csv.bz2``.
- ``fars_read()`` reads a csv under the specified file path.
- ``fars_read_years()`` combines ``make_filename()`` and ``fars_read()`` and reads CSVs of all years specified. Note that the CSVs need to follow the pattern "accident_YEAR.csv.bz2" and they need to be located in the working directory.


## Summarize Years 

``fars_summarize_years()`` uses  ``fars_read_years()`` under the hood to read data of all years specified and then counts the number observations per month. 

```{r}
# Summarise Multiple Years
fars_summarize_years(years = c("2013", "2014", "2015"))

```


## Plot Accidents of a State

``fars_map_state()`` uses ``make_filename()`` ``fars_read()`` under the hood to create and read the path of the csv for the specified year. A state of interest needs to be selected via argument ``state.num`` and then the accidents of this state are plotted on a map. Below the accidents for state number "13" in 2013 are plotted. 

```{r}
# Summarise Multiple Years
fars_map_state(state.num = 13, year = "2013")
```
